Mining of Keystroke and Mouse Dynamics to Increase the Engagement of Students with Programming Assignments

### 2018-04-20 paper.tex
subsub fixed

\subsubsection{Capturing the Keystroke and Mouse Data}
As it was explained before, as a student is trying to solve an assignment,
a script coded in JavaScript runs in the background,
capturing every keystroke, mouse movement and mouse button pressed. Each record
of these events includes a time-stamp in milliseconds (using the method
getTime() of JavaScript\'s built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device. Programming assignments are
evaluated using unit tests; the results of the evaluation are shown to users.
If all tests the program is considered to be correct. The source code for the
Protoboard web based learning environment including the KD and MD functions are
open source and available as Github repositories
at\url{https://github.com/amherag/keyboard-mouse-dynamics}; the code for the
sandbox is also available in \url{https://github.com/mariosky/sandbox}.

@@

\subsubsection{Preprocessing of the Keystroke and Mouse Data}

>>>>

\subsection{Capturing the Keystroke and Mouse Data}
As it was explained before, as a student is trying to solve an assignment,
a script coded in JavaScript runs in the background,
capturing every keystroke, mouse movement and mouse button pressed. Each record
of these events includes a time-stamp in milliseconds (using the method
getTime() of JavaScript\'s built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device. Programming assignments are
evaluated using unit tests; the results of the evaluation are shown to users.
If all tests the program is considered to be correct. The source code for the
Protoboard web based learning environment including the KD and MD functions are
open source and available as Github repositories
at\url{https://github.com/amherag/keyboard-mouse-dynamics}; the code for the
sandbox is also available in \url{https://github.com/mariosky/sandbox}.

@@

\subsection{Preprocessing of the Keystroke and Mouse Data}
